\section{Bibliography}
\label{chap:Bibliography}

\label{Bib:The Elements Of Statistical Learning DataMining}[1] T. Hastie, R. Tibshirani, J. Friedman. \textit{The Elements of Statistical Learning data mining, inference, and prediction}. \textbf{2nd edition}. Springer; New York, USA. 2017.\\

\label{Bib:Python Machine Learning}\noindent [2] Sebastian Raschka, Vahid Mirjalili. \textit{Python Machine Learning}. \textbf{2nd edition}. Packt; Birmingham, UK. 2017.\\

\label{Bib:Hands-on Machine Learning}\noindent [3] Aurélien Géron. \textit{Hands-On Machine Learning with Scikit-Learn and TensorFlow}. O'Reilly Media; Sebastopol, CA. 2017.\\

\label{Bib:Week40Notes}\noindent [4] University of Oslo. "Week 40: From Stochastic Gradient Descent to Neural networks". Department of Physics, University of Oslo. \href{https://compphysics.github.io/MachineLearning/doc/pub/week40/html/week40.html}{https://compphysics.github.io/MachineLearning/doc/pub/week}
\href{https://compphysics.github.io/MachineLearning/doc/pub/week40/html/week40.html}{40/html/week40.html}. (Oct 6, 2020)\\

\label{Bib:Week41Notes}\noindent [5] University of Oslo. "Week 41 Tensor flow and Deep Learning, Convolutional Neural Networks". Department of Physics, University of Oslo. \href{https://compphysics.github.io/MachineLearning/doc/pub/week41/html/week41.html}{https://compphysics.github.io/MachineLearning/doc/p}
\href{https://compphysics.github.io/MachineLearning/doc/pub/week41/html/week41.html}{ub/week41/html/week41.html}. (Oct 10, 2020)\\
