\section{Bibliography}
\label{chap:Bibliography}

\label{Bib:T. Hastie, R. Tibshirani, J. Friedman}[1] T. Hastie, R. Tibshirani, J. Friedman. \textit{The Elements of Statistical Learning data mining, inference, and prediction}; 2nd edition; Springer; New York, USA. 2017.\\

\label{Bib:Sebastian Raschka, Vahid Mirjalili}\noindent [2] Sebastian Raschka, Vahid Mirjalili. \textit{Python Machine Learning}; 2nd edition; Packt; Birmingham, UK. 2017.\\

\label{Bib:Aurelien Geron}\noindent [3] Aurélien Géron. \textit{Hands-On Machine Learning with Scikit-Learn and TensorFlow}; O'Reilly Media; Sebastopol, CA. 2017.\\

\label{Bib:Lopez de Prado}\noindent [4] Lopez de Prado, Marcos. \textit{Advances in Financial Machine Learning}; Wiley; New Jersey; 2018.\\

\label{Bib:Leonardo C. Martinez, Diego N. da Hora, Joao R. de M. Palotti, Wagner Meira Jr. and Gisele L. Pappa}\noindent [5] \textit{From an Artificial Neural Network to a Stock Market Day-Trading System: A Case Study on the BMF BOVESPA}; Leonardo C. Martinez, Diego N. da Hora, Joao R. de M. Palotti, Wagner Meira Jr. and Gisele L. Pappa (2009).\\

\label{Bib:Van-Dai Ta, Chuan-Ming Liu, Direselign Addis Tadesse}\noindent [6] \textit{Portfolio Optimization-Based Stock Prediction Using
Long-Short Term Memory Network in Quantitative
Trading}; Van-Dai Ta, Chuan-Ming Liu, Direselign Addis Tadesse (2020).\\

\label{Bib:Week42Notes}\noindent [7] University of Oslo. \textit{Week 42 Convolutional (CNN) and Recurrent (RNN) Neural Networks}. Department of Physics, University of Oslo. \href{https://compphysics.github.io/MachineLearning/doc/pub/week42/html/week42.html}{https://compphysics.github.io/MachineLearning/doc/p}
\href{https://compphysics.github.io/MachineLearning/doc/pub/week41/html/week41.html}{ub/week42/html/week42.html}. (Oct 17, 2020)\\

\label{Bib:b3 quotes}\noindent [8] B3 - Sao Paulo's stock exchange. \href{http://www.b3.com.br/en_us/market-data-and-indices/data-services/market-data/quotes/quotes/}{http://www.b3.com.br/en\_us/market-data-and-indices/data-services/market-data/quotes/quotes/}\\

\label{Bib:Hyndman, R.J., and Athanasopoulos, G.}\noindent [9] Hyndman, R.J., and Athanasopoulos, G. (2018) Forecasting: principles and practice, 2nd edition, OTexts: Melbourne, Australia. \href{https://otexts.com/fpp2/}{otexts.com/fpp2/}. Accessed on 07.12.2020.
